Study of the numerical solution of X-Modes equations around the hybrid resonance

### 2015-01-28 report/absorption.tex
1) bug fix 2) new pics 3) conclusions

\subsection{Limiting Amplitude and Limiting Absorption Principle}
In this section we perform several numerical experiments,
with the normalization chosen as $\epsilon_0=\mu_0=1$, $\omega=c=1$. 
Also, we set $m_e=1$ and $e=-1$. From this it follows that $w_c=-B_0$ and $w_p^2=N_e$. 
We consider the following two cases:
\begin{itemize}
 \item case $N_e\neq \operatorname{const}$, no resonance;
 \item case $N_e\neq \operatorname{const}$, resonance.
\end{itemize}
For every fixed absorption rate $\nu$, in the time domain we choose the boundary conditions of the form
\begin{align}
\label{eq:bcs}
\left.\partial_t H\right|_{x=-L}&=-\left.\partial_x E_y\right|_{x=-L}=G\sin(t),\; G\in \mathbb{R}, \\
 \nonumber
 \left.\partial_t H\right|_{x=H}&=0,
\end{align}
and zero initial conditions, and in the frequency domain
\bealn
 \left.\partial_x \hat{E}_y\right|_{x=-L}&=G,\\
 \left.\partial_x \hat{E}_y\right|_{x=H}&=0.
\eealn
We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain (the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain. 
In the numerical experiments we check whether the following two quantities
\ben
\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right)
\een
are close as $\nu\rightarrow 0$ (provided that the first of these quantities exists). 
\subsubsection{No-Resonance Case}
We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}$ satisfies 
the Airy equation.

We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$. 
In all the experiments in this section the CFL number=0.5.

@@

\begin{figure}[htb]
\includegraphics[width=0.85\textwidth]{airy/figure_nu1e2-crop.pdf}
\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time for $t\rightarrow +\infty$.}
 \label{fig:nu1e2_harmon}
\end{figure}

In Fig.~\ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\hat{E}_y^{\nu}\mathrm{e}^{it}$, for
fixed values of $t$. Both solutions appear to be in close agreement. 
\begin{figure}[htb]
 \begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{airy/figure_nu1e2_2-crop.pdf}
&
\includegraphics[width=0.45\textwidth]{airy/figure_error_nu1e4-crop.pdf}\\
\end{tabular}
\caption{In the left figure we show the solution for $\nu=10^{-2}$, for two fixed moment of times. In the right figure 
the dependence of the error (\ref{eq:error}) on time for $\nu=10^{-4}$ is demonstrated. 
We can see that the error is decreasing on the given time interval.}
 \label{fig:nu1e2_harmon2}
\end{figure}
\FloatBarrier
The computed $L_2$ error
\begin{align}
\label{eq:error}
\mathcal{E}_{x,y}(t)=\|\Im\left(\hat{E}_{x,y}^{\nu}\exp(it)\right)-E_{x,y}^{\nu}(t)\|_{L_{y}(-L;H)}.
\end{align}
for $\nu=10^{-2}$ did not exceed 1.1e-3 for values of $t\in \left(28501,  30000\right)$.

Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$. As previously, 
to demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
inside the domain and plot 
the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
The error (\ref{eq:error}) for $\nu=1e-4$ at the time interval $[228000.05,\; 240000.05]$ does not exceed 2.8e-4. 
One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution, 
c.f. e.g. Fig.~\ref{fig:nu1e2_harmon2}. 
For $\nu=10^{-4}$ we were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$, 
see also Fig.~\ref{fig:nu1e2_harmon2}(right). 
For example, for $\nu=10^{-6}$ we were not able to reach the limiting amplitude solution even on the time interval $t\leq 1.92e6$, 
see Fig.~\ref{fig:nu1e4_harmon} (right). 
\begin{figure}
\begin{tabular}{cc}
 \includegraphics[width=0.5\textwidth]{airy/figure_nu1e4-crop.pdf}&
 \includegraphics[width=0.5\textwidth]{airy/figure_nu1e6-crop.pdf}\\
\end{tabular}
\caption{In the upper figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
In the lower figure we show the solution for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
$\nu=10^{-4}$ the limiting amplitude solution was reached for large $t$. For $\nu=10^{-6}$ we were not able 
to obtain the limiting amplitude solution even for $t\approx 1.9e6$. }
  \label{fig:nu1e4_harmon}
\end{figure}

@@

We compare the results for $\nu=10^{-2},\; 10^{-3}$ in Fig. \ref{fig:resonance_nus_ex_x}, 
\ref{fig:resonance_nus_ey_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}. 
%In the time domain, we chose the discretization size $\Delta x=0.025$. 
The harmonic dependence of the solution on time is demonstrated by fixing $x_c$ inside the domain and plotting 
$E_x^{\nu}(x_c,t)$ and $E_y^{\nu}(x_c, t)$ for a range of $t$. We compare these solutions to $\Im\left(\hat{E}_x^{\nu}(x_c)\mathrm{e}^{it}\right)$ and 
$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right)$. In the former case we choose the point $x_c=0$, where the resonance occurs.

\begin{figure}
\begin{tabular}{cc}
\includegraphics[width=0.5\textwidth]{res/ex_fixed_x-crop.pdf}&
\includegraphics[width=0.5\textwidth]{res/ex_fixed_x_1e3-crop.pdf}
\end{tabular}
\caption{The figures demonstrate the dependence of the solutions 
$E_x^{\nu}(0,t)$ on time $t$ for different values of $\nu$. }
\label{fig:resonance_nus_ex_x}
\end{figure}
\begin{figure}
\begin{tabular}{cc}
\includegraphics[width=0.5\textwidth]{res/ey_fixed_x-crop.pdf}&
\includegraphics[width=0.5\textwidth]{res/ey_fixed_x_1e3-crop.pdf}
 \end{tabular}
\caption{The figures demonstrate the dependence of the solutions 
$E_y^{\nu}(-2.5125,t)$ on time $t$ for different values of $\nu$. }
\label{fig:resonance_nus_ey_x}
\end{figure}

\begin{figure}
\begin{tabular}{cc}
\includegraphics[width=0.5\textwidth]{res/ex_fixed_t-crop.pdf}&
\includegraphics[width=0.5\textwidth]{res/ex_fixed_t_1e3-crop.pdf}
\end{tabular}
\caption{The figures demonstrate the dependence of the solutions 
$E_y^{\nu}(x,t)$ on $x$ for fixed values of $t$. }
\label{fig:resonance_nus_ex_t}
\end{figure}
\begin{figure}
\begin{tabular}{cc}
\includegraphics[width=0.5\textwidth]{res/ey_fixed_t-crop.pdf}&
\includegraphics[width=0.5\textwidth]{res/ey_fixed_t_1e3-crop.pdf}
 \end{tabular}
\caption{The figures demonstrate the dependence of the solutions 
$E_y^{\nu}(x,t)$ on $x$ for fixed values of $t$. }
\label{fig:resonance_nus_ey_t}
\end{figure}

>>>>

\subsection{Limiting Amplitude and Limiting Absorption Principle}
In this section we perform several numerical experiments,
with the normalization chosen as $\epsilon_0=\mu_0=1$, $\omega=c=1$. 
Also, we set $m_e=1$ and $e=-1$. From this it follows that $w_c=-B_0$ and $w_p^2=N_e$. 
We consider the following two cases:
\begin{itemize}
 \item case $N_e\neq \operatorname{const}$, no resonance;
 \item case $N_e\neq \operatorname{const}$, resonance.
\end{itemize}
For every fixed absorption rate $\nu$, in the time domain we choose the boundary conditions of the form
\begin{align}
\label{eq:bcs}
\left.\partial_t H\right|_{x=-L}&=-\left.\partial_x E_y\right|_{x=-L}=G\sin(t),\; G\in \mathbb{R}, \\
 \nonumber
 \left.\partial_t H\right|_{x=H}&=0,
\end{align}
and zero initial conditions, and in the frequency domain
\bealn
 \left.\partial_x \hat{E}_y\right|_{x=-L}=G,\; \left.\partial_x \hat{E}_y\right|_{x=H}=0.
\eealn
We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain (the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain. 
In the numerical experiments we check whether the following two quantities
\ben
\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right)
\een
are close as $\nu\rightarrow 0$ (provided that the first of these quantities exists). 
\subsubsection{No-Resonance Case}
We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}^{\nu},\; \nu=0,$ satisfies 
the Airy equation, c.f. also Remark \ref{remark:other}.

We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$.

@@

\begin{figure}[htb]
\includegraphics[width=0.85\textwidth]{airy/figure_nu1e2-crop.pdf}
\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time for large times.}
 \label{fig:nu1e2_harmon}
\end{figure}

In Fig.~\ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{it}\right)$, for
fixed values of $t$. Both solutions appear to be in close agreement. 
\begin{figure}[htb]
 \begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{airy/figure_nu1e2_2-crop.pdf}
&
\includegraphics[width=0.45\textwidth]{airy/figure_error_nu1e4-crop.pdf}\\
\end{tabular}
\caption{In the left figure we show the solution for $\nu=10^{-2}$, for two fixed moment of times. In the right figure 
the dependence of the error (\ref{eq:error}) on time for $\nu=10^{-4}$ is demonstrated. 
We can see that the error is decreasing on the given time interval.}
 \label{fig:nu1e2_harmon2}
\end{figure}
\FloatBarrier
The computed $L_2$ error
\begin{align}
\label{eq:error}
\mathcal{E}_{x,y}(t)=\|\Im\left(\hat{E}_{x,y}^{\nu}\exp(it)\right)-E_{x,y}^{\nu}(t)\|_{L_{2}(-L;H)}.
\end{align}
for $\nu=10^{-2}$ did not exceed 1.1e-3 for values of $t\in \left(28501,  30000\right)$.

Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$. As previously, 
to demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
inside the domain and plot 
the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
The error (\ref{eq:error}) for $\nu=1e-4$ at the time interval $[228000.05,\; 240000.05]$ does not exceed 2.8e-4. 
One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution. 
For $\nu=10^{-4}$ we were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$, 
see also Fig.~\ref{fig:nu1e2_harmon2}(right). 
For example, for $\nu=10^{-6}$ we were not able to reach the limiting amplitude solution even on the time interval $t\leq 1.92e6$, 
see Fig.~\ref{fig:nu1e4_harmon} (right). 
\begin{figure}
\begin{tabular}{cc}
 \includegraphics[width=0.45\textwidth]{airy/figure_nu1e4-crop.pdf}&
 \includegraphics[width=0.45\textwidth]{airy/figure_nu1e6-crop.pdf}\\
\end{tabular}
\caption{In the left figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
In the right figure we show the solution for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
$\nu=10^{-4}$ the limiting amplitude solution was reached for large $t$. For $\nu=10^{-6}$ we were not able 
to obtain the limiting amplitude solution even for $t\approx 1.9e6$. }
  \label{fig:nu1e4_harmon}
\end{figure}

@@

We compare the results for $\nu=10^{-2},\; 10^{-3},\; 10^{-4}$ in Fig. \ref{fig:resonance_nus_ex_x}, 
\ref{fig:resonance_nus_ey_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t}. 
%In the time domain, we chose the discretization size $\Delta x=0.025$. 
The harmonic dependence of the solution on time is demonstrated by fixing $x_c$ inside the domain and plotting 
$E_x^{\nu}(x_c,t)$ and $E_y^{\nu}(x_c, t)$ for a range of $t$. We compare these solutions to $\Im\left(\hat{E}_x^{\nu}(x_c)\mathrm{e}^{it}\right)$ and 
$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right)$. In the former case we choose the point $x_c=0$, where the resonance occurs.

\begin{figure}
\begin{tabular}{cc}
\includegraphics[width=0.5\textwidth]{res/ey_fixed_x-crop.pdf}&
\includegraphics[width=0.5\textwidth]{res/ey_fixed_x_1e3-crop.pdf}
 \end{tabular}
\caption{The figures demonstrate the dependence of the solutions 
$E_y^{\nu}(-2.5125,t)$ on time $t$ for different values of $\nu$. }
\label{fig:resonance_nus_ey_x}
\end{figure}
\begin{figure}
 \includegraphics[width=0.8\textwidth]{res/ex_fixed_x_nu1e4-crop.pdf}
 \caption{The plot shows the dependence of the solution $E_x^{\nu}(x_c,t),\;\nu=10^{-4}$ on time $t$ for fixed 
 $x_c=0.0125$ and for $x_c=-2.5$. We can see that the solutions computed in the time domain are in close agreement 
 with the solution computed in the frequency domain at the point $x_c=-2.5$, however, differ at the point $0.0125$ which is 
 close to the $x=0$ where the resonance occurs.}
 \label{fig:resonance_nus_ex_x}
\end{figure}
\begin{figure}
\begin{tabular}{cc}
\includegraphics[width=0.5\textwidth]{res/ex_fixed_t-crop.pdf}&
\includegraphics[width=0.5\textwidth]{res/ex_fixed_t_1e3-crop.pdf}
\end{tabular}
\caption{The figures demonstrate the dependence of the solutions 
$E_x^{\nu}(x,t)$ on $x$ for fixed values of $t$. }
\label{fig:resonance_nus_ex_t}
\end{figure}
\begin{figure}
\includegraphics[width=0.45\textwidth]{res/ey_fixed_t_1e3-crop.pdf}
\includegraphics[width=0.55\textwidth]{res/ey_fixed_x_nu1e4-crop.pdf}
\caption{The left figure demonstrates the dependence of the solution  
$E_y^{\nu}(x,y)$ on $x$ for fixed values of $t$. For a chosen value of $\nu$ the solutions computed in the time domain are in close agreement 
to the solutions computed in the frequency domain (this seem to be only partially 
true for the computed values $E_x^{\nu}(x,y)$ in this case (which also may be caused by the discretization). 
The right figure shows the dependence of the solution $E_y^{\nu}(x,t)$ for $\nu=10^{-4}$ on time for fixed $x=x_c$. 
We can see that the while the limiting amplitude principle holds true, the difference between the solutions computed in 
the time and frequency domain is noticeable on this scale. 
}
\label{fig:resonance_nus_ey_t}
\end{figure}

\begin{figure}
\includegraphics[width=0.95\textwidth]{res/ex_fixed_t_1e4_2-crop.pdf}
\caption{The figures demonstrate the dependence of the solutions 
$E_x^{\nu}(x,t)$ and $E_y^{\nu}(x,y)$ on $x$ for fixed values of $t$. While the solution in the time-domain 
in the resonance point $x=0$ has a smaller absolute value than that computed in the frequency domain (in the plot both solutions are truncated to 
axis limits), in other points the values are rather close. }
\label{fig:resonance_nus_eyx_t}
\end{figure}

### 2015-01-28 report/numerics.tex
1) bug fix 2) new pics 3) conclusions

The second part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of our frequency domain code 
and of the time domain code (computed for large values of time). 
The time-domain code implements the scheme described in Section \ref{sec:discr} and 
is written in Fortran. 
\subsection{Frequency Domain Problem}
\label{sec:freq_dep}
\subsubsection{Validity of the Implementation}
To check the validity of the code, we perform a numerical experiment with (formally chosen) parameters:
\begin{align}
\label{eq:parameters}
\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}.
\end{align}
Additionally, the boundary conditions read as 
\bealn
\label{eq:bcs_airy}
\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2iAi(-L)+Ai'(-L),\\
\partial_{1}E_{y}(H)=0,
\eealn
where $Ai(x)$ is the Airy function. 
For more detail on Airy functions and the Airy equation see \cite[Chapter 10.4]{abramowitz_stegun}. 
It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain}) in 1D, with the Fourier variable $\theta=0$ (see (\ref{vf1dcase}), and $\nu=0$, 
satisfies the Airy equation, and hence, 
with the choice of the boundary conditions as above, we obtain that 
\bealn
E_{y}=Ai(x),\qquad 
E_{x}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)
\eealn
is the solution to the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs_airy}). 
The well-posedness of the respective variational formulation is due to Remark \ref{remark:other}.

@@

@@

@@

    	width=0.5\textwidth,

@@

@@

Denoting by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on the finest mesh, let 
\begin{align}
\label{eq:def_epsilon}
h_{\epsilon}=\sup\{h: \|E_{x}^{h'}-E_{x}^{c}\|<\epsilon \text{ for all } h'<h\}.
\end{align}
The computed dependence of $h_{\epsilon}$ on $\nu$ is shown in Fig.~\ref{fig:dependence}.
\begin{figure}
\begin{tabular}{cc}
\begin{tikzpicture}
    \begin{loglogaxis}[
    	width=0.5\textwidth,
    	height=0.5\textwidth,
        xlabel=$\nu$,
        ylabel=$h_{\epsilon}$,
        legend style={
at={(0.2,1.5)},
legend pos= south east,
anchor=south east, 
draw=none
}
]
\addplot[mark=*,blue] table {pics/h1e-1.dat}; 
\addlegendentry{$\epsilon=1e-1$};
%\addplot[mark=o,red] table {pics/h1e-2.dat}; 
%\addlegendentry{$\epsilon=1e-2$};
\addplot[mark=triangle,green] table {pics/h1e-3.dat}; 
\addlegendentry{$\epsilon=1e-3$};
%\addplot[mark=square,cyan] table {pics/h1e-4.dat}; 
%\addlegendentry{$\epsilon=1e-4$};
\addplot[dashed, red] table {pics/nu1.dat}; 
\addlegendentry{$O(\nu)$};
\addplot[dashed, blue] table {pics/nu32.dat}; 
\addlegendentry{$O(\nu^{\frac{3}{2}})$};
\end{loglogaxis}
\end{tikzpicture} 
&
\includegraphics[width=0.5\textwidth]{figure1-crop.pdf}
\end{tabular}
\caption{In the left figure the depenence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated. 
In the right figure we show the solutions for the problem for different values of $\nu$. }
\label{fig:dependence}
\end{figure}
We can see that the estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
at least for a given value of $\epsilon$.

@@

\FloatBarrier
\paragraph{Condition Number}

We consider the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
on $\nu$, for several values of $h$ (see Table \ref{tab:cond_number}).
\begin{table}[ht!]
\begin{tabular}{c|ccccccccc}
\diagbox[width=10em]{$h$}{$\nu$}& 100 & 10 & 1 & 0.1 & 1e-2 & 1e-3 & 1e-4 & 1e-8 & 0\\
 \hline
1 & 3.9634&4.3787 &4.987&36.949&42.394& 42.757 &42.79&42.793&42.793\\
\hline
0.5&      3.9931& 6.87&48.473 & 168.41  &207.34  & 209.63 & 209.83 & 209.85&  209.85\\
\hline
 0.1&      16.09  &     159.56  &     1146.1   &    8304.1   &     19169  &      20270   &     20344   &     20352   &     20352\\
 \hline
0.05&      64.046  &     637.18  &     4686.2   &     38876 &  1.4e5 &  1.58e5 &   1.58e5 &  1.58e5 &  1.58e5\\
\hline
 0.01&       1600    &   15921 & 1.2e5  & 1.1e6 & 8.3e6  & 1.8e7   & 1.93e7  & 1.93e7  & 1.93e7\\
\end{tabular}
\caption{The condition number of the matrix of the system (\ref{eq:simple_system}) for different values of $\nu$ and $h$. }
\label{tab:cond_number}
\end{table}
Remarkably, for $\nu=0$ the computed matrices are not singular. \urev{We do not know the exact reason for such a behavior.}
As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}. 
\begin{figure}
 \includegraphics[width=0.4\textwidth]{figure2-crop.pdf}
 \caption{The plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for meshes that are coarse 
 with respect to $\nu$ (e.g. $\nu=10^{-4}, \; h=10^{-2}$, or $\nu=0,\; h=10^{-2}$), the computed solution seems to be only piecewise-continuous in $\nu$, 
 while for finer meshes and $\nu>0$ the solution seems to be smooth. It can be also seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
 computed for $\nu=0$ are indistinguishable on this scale.}
 \label{fig:small_nu}
\end{figure}

>>>>

The second part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of our frequency domain code 
and of the time domain code (computed for large values of time). 
The time-domain code implements the scheme described in Section \ref{sec:discr} and 
is written in Fortran. 
\subsection{Frequency Domain Problem}
\label{sec:freq_dep}
\subsubsection{Validity of the Implementation}
To check the validity of the code, we perform a numerical experiment with (formally chosen) parameters:
\begin{align}
\label{eq:parameters}
\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}.
\end{align}
Additionally, the boundary conditions read as 
\begin{align}
\label{eq:bcs_airy}
\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2iAi(-L)+Ai'(-L),\\
\partial_{1}E_{y}(H)=0,
\end{align}
where $Ai(x)$ is the Airy function. 
For more detail on Airy functions and the Airy equation see \cite[Chapter 10.4]{abramowitz_stegun}. 
It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain}) in 1D, with the Fourier variable $\theta=0$ (see (\ref{vf1dcase}), and $\nu=0$, 
satisfies the Airy equation, and hence, 
with the choice of the boundary conditions as above, we obtain that 
\bealn
E_{y}=Ai(x),\qquad 
E_{x}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)
\eealn
is the solution to the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs_airy}). 
The well-posedness of the respective variational formulation is due to Remark \ref{remark:other}.

@@

\begin{align*}

@@

\end{align*}

@@

    	width=0.45\textwidth,

@@

        ymin=1e-10,

@@

Denoting by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on the finest mesh, let 
\begin{align}
\label{eq:def_epsilon}
h_{\epsilon}=\sup\{h: \|E_{x}^{h'}-E_{x}^{c}\|<\epsilon \text{ for all } h'<h\}.
\end{align}
The computed dependence of $h_{\epsilon}$ on $\nu$ is shown in Fig.~\ref{fig:dependence}.
\begin{figure}
\begin{tabular}{cc}
\begin{tikzpicture}
    \begin{loglogaxis}[
    	width=0.4\textwidth,
    	height=0.4\textwidth,
        xlabel=$\nu$,
        ylabel=$h_{\epsilon}$,
        legend style={
at={(0.2,1.5)},
legend pos=north west,
%anchor=south east, 
draw=none
}
]
\addplot[mark=*,blue] table {pics/h1e-1.dat}; 
\addlegendentry{$\epsilon=1e-1$};
%\addplot[mark=o,red] table {pics/h1e-2.dat}; 
%\addlegendentry{$\epsilon=1e-2$};
\addplot[mark=triangle,green] table {pics/h1e-3.dat}; 
\addlegendentry{$\epsilon=1e-3$};
%\addplot[mark=square,cyan] table {pics/h1e-4.dat}; 
%\addlegendentry{$\epsilon=1e-4$};
\addplot[dashed, red] table {pics/nu1.dat}; 
\addlegendentry{$O(\nu)$};
\addplot[dashed, blue] table {pics/nu32.dat}; 
\addlegendentry{$O(\nu^{\frac{3}{2}})$};
\end{loglogaxis}
\end{tikzpicture} 
&
\includegraphics[width=0.4\textwidth]{figure1-crop.pdf}
\end{tabular}
\caption{In the left figure the depenence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated. 
In the right figure we show the computed solutions for the problem with parameters in Table \ref{tab:parameters} for different values of $\nu$. }
\label{fig:dependence}
\end{figure}
We can see that the estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
at least for a given value of $\epsilon$.

@@

\FloatBarrier
\paragraph{Condition Number}
In Table \ref{tab:cond_number} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
on $\nu$, for several values of $h$.
\begin{table}[ht!]
\begin{tabular}{c|ccccccccc}
\diagbox[width=10em]{$h$}{$\nu$}& 100 & 10 & 1 & 0.1 & 1e-2 & 1e-3 & 1e-4 & 1e-8 & 0\\
 \hline
1 & 3.9634&4.3787 &4.987&36.949&42.394& 42.757 &42.79&42.793&42.793\\
\hline
0.5&      3.9931& 6.87&48.473 & 168.41  &207.34  & 209.63 & 209.83 & 209.85&  209.85\\
\hline
 0.1&      16.09  &     159.56  &     1146.1   &    8304.1   &     19169  &      20270   &     20344   &     20352   &     20352\\
 \hline
0.05&      64.046  &     637.18  &     4686.2   &     38876 &  1.4e5 &  1.58e5 &   1.58e5 &  1.58e5 &  1.58e5\\
\hline
 0.01&       1600    &   15921 & 1.2e5  & 1.1e6 & 8.3e6  & 1.8e7   & 1.93e7  & 1.93e7  & 1.93e7\\
\end{tabular}
\caption{The condition number of the matrix of the system (\ref{eq:simple_system}) for different values of $\nu$ and $h$. }
\label{tab:cond_number}
\end{table}
Remarkably, for $\nu=0$ the computed matrices are not singular. \urev{We do not know the exact reason for this.}
As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}. 
\begin{figure}
 \includegraphics[width=0.4\textwidth]{figure2-crop.pdf}
 \caption{The plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for meshes that are coarse 
 with respect to $\nu$ (e.g. $\nu=10^{-4}, \; h=10^{-2}$, or $\nu=0,\; h=10^{-2}$), the computed solution seems to be only piecewise-continuous in $\nu$, 
 while for finer meshes and $\nu>0$ the solution seems to be smooth. It can be also seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
 computed for $\nu=0$ are indistinguishable on this scale.}
 \label{fig:small_nu}
\end{figure}
